---
title: "Lab 1"
author: "Author Name"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

Make sure to load our important packages by running the following code:

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

In this lab assignment, we apply some techniques of exploratory data analysis (EDA) that we've studied to examine movie data from [the Tidy Tuesday project](https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-03-09).

Our first step is to load our data using the `readr` package, run the following command:

```{r}
# Read in data
movies <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/movies.csv')
# Some data cleaning 
movies <- movies %>% drop_na(imdb_rating)
movies <- movies %>% mutate(foreign_film=ifelse(country=="USA","US","Foreign"))
```

### Exercise 1

Use the `dim` command to determine the number of rows and columns that are in the data set.

```{r data_dim}
# Insert code for Exercise 1 here
```

Number of columns =

Number of rows =

### Exercise 2

Use the `glimpse` command to get an idea of the types for all of the variables in the data set.

```{r data_glimpse}
# Insert code for Exercise 2 here
```

Variable type for `budget_2013` is = ?

Variable type for `rated` is = ?

Variable type for `imdb_rating` is = ?

### Exercise 3

Run the following command to obtain a frequency table for the `rate` variable:

```{r table}
table(movies$rated)
```

Number of levels for the `rated` variable = ?

### Exercise 4

Load the `ggformula` package in order to use the plotting functions we have covered.

```{r load_package}
# Insert code here
```

Create a barplot to provide an visual representation of the frequency table obtained in the last exercise.

```{r load_package}
# Insert code here
```

Of the different movie ratings, the most common one is = ?

### Exercise 5

Complete the code to compute the mean and median values for the `budget_2013` and `imdb_rating` variables.

```{r descr_stats}
# Uncomment the next four lines and complete the code
#budget_mean <- 
#budget_median <- 
#imdb_mean <- 
#imdb_median <- 
```


### Exercise 6

The following code produces a histogram for the `budget_2013` variable:
```{r budget_hist}
gf_histogram(~budget_2013,data=movies)
```

Describe the shape of this distribution. 



Do you think the median of the `budget_2013` variable is greater or less then the mean of the `budget_2013` variable? 


Uncomment and run the following code to check your answer to the last question:
```{r budget_check}
#(budget_mean)
#(budget_median)
```

### Exercise 7
Create a histogram for the `imdb_rating` variable.
```{r ir_hist}
# Insert code for Exercise 7 here
```

Based on the plot you obtain, is the data best described as left skewed, symmetric, or right skewed? 

### Exercise 8

Compute the standard deviation for the `budget_2013` and `imdb_rating` variables.
```{r variances}
# Insert code for Exercise 8 here
```


### Exercise 9

Obtain a boxplot for the `budget_2013` variable? 
```{r budget_box}
# Insert code here
```

Does the boxplot show any outliers for the `budget_2013` variable? 


Obtain a boxplot for the `imdb_rating` variable? 
```{r ir_box}
# Insert code here
```

Does the boxplot show any outliers for the `imdb_rating` variable? 


Use the boxplot for the `imdb_rating` variable to estimate its IQR value. 

Compute the IQR for the `imdb_rating` variable. 
```{r ir_iqr_box}
# Insert code here
```

### Exercise 10

The following scatterplot show the  `imdb_rating` variable versus the `budget_2013` variable.
```{r scatter}
gf_point(imdb_rating~budget_2013,data=movies)
```

Describe what this plot informs us on regarding any association between to two variables. 


### Exercise 11

The following code outputs the mean value for the `budget_2013` variable grouped by the rating for the movies. 
```{r grouped}
movies %>% group_by(rated) %>% summarise(avg_budget=mean(budget_2013))
```

What conclusions do you draw from the information provided by the result obtained from running the previous command? 



### Exercise 12

The following code produces a mosaic plot that shows the relationship between two categorical variables. One lists if a movie if rated G, PG, PG-13, or R; and the other lists whether the movie is a foreign film or made in the United States (i.e. domestic):
```{r}
movies %>% filter(rated %in% c("G","R","PG-13","PG")) %>% ggplot() + 
  geom_mosaic(aes(x=product(rated,foreign_film),fill=foreign_film)) + theme(legend.position = "none")
```

Describe what the mosaic plot shows.


Of the films that are G-rated, are more of them foreign or domestic?

Of the films that are domestic, are more of them PG-rated or PG-13 rated? 

