---
title: "Homework 2"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tidyverse)
library(learnr)
library(openintro)
library(gradethis)
tutorial_options(exercise.timelimit = 60, exercise.checker = gradethis::grade_learnr)
```


## Instructions

This homework is meant to provide practice with those aspects of R programming introduced during the second lecture. Be sure to take your time and try to understand what each of the R commands in this homework set does. 

## Using R as a calculator

The exercises in this section provide practice in using R as a simple calculator. 

### Exercise 1

Use R code to compute a value for the expression $10\left(1 - \frac{3}{2}\right)$. 


```{r calc_ex_1, exercise = TRUE}

```

```{r calc_ex_1-solution}
10*(1 - 3/2)
```

```{r calc_ex_1-check}
grade_code()
```

### Exercise 2

Use R to compute a value for the expression $2^8 - \sqrt{16}$. 

```{r calc_ex_2, exercise = TRUE}

```

```{r calc_ex_2-solution}
2^8 - sqrt(16)
```

```{r calc_ex_2-check}
grade_code()
```

### Exercise 3

Insert parentheses in the appropriate place(s) to obtain a value of 2. 

```{r calc_ex_3, exercise = TRUE, exercise.eval = TRUE}
2 * 3 +  4 * 2 - 6 / 2*3/ 2 * 5

```

```{r calc_ex_3-solution}
2 * (3 +  4 * 2 - 6 / (2*3))/ (2 * 5)

```

```{r calc_ex_3-check}
grade_code()
```


## Single-variable numerical data 

The exercises in this section provide practice with working with one-variable numerical data in R. 

### Exercise 1

Create a vector containing the numerical values 4.7, 8.3, 5.6, 6.9, 9.4, 8.3, and 7.1, and store it in a variable named `my_data`. 
```{r nd_ex_1, exercise = TRUE}

```

```{r nd_ex_1-solution}
my_data <- c(4.7, 8.3, 5.6, 6.9, 9.4, 8.3, 7.1)

```

```{r nd_ex_1-check}
grade_code()
```

### Exercise 2
Compute the length of the vector assigned to the variable `my_data`. 
```{r nd_ex_2-setup}
my_data <- c(4.7, 8.3, 5.6, 6.9, 9.4, 8.3, 7.1)

```


```{r nd_ex_2, exercise = TRUE}

```

```{r nd_ex_2-solution}
length(my_data)

```

```{r nd_ex_2-check}
grade_code()
```

### Exercise 3

Compute the mean of the data assigned to the variable `my_data`. 
```{r nd_ex_3-setup}
my_data <- c(4.7, 8.3, 5.6, 6.9, 9.4, 8.3, 7.1)

```


```{r nd_ex_3, exercise = TRUE}

```

```{r nd_ex_3-solution}
mean(my_data)

```

```{r nd_ex_3-check}
grade_code()
```


## Single-variabel categorical data

The exercises in this section provide practice with working with one-variable categorical data in R. 

### Exercise 1

Suppose we have data consisting of t-shirt sizes for 8 individuals with 3 size S, 4 size M, and 1 sise L. Create a factor in R to store this data and assign it to a variable named `t_sizes`. 

```{r fct_ex_1, exercise = TRUE}

```

```{r fct_ex_1-solution}
t_sizes <- factor(c("S","S","S","M","M","M","M","L"))

```

```{r fct_ex_1-check}
grade_code()
```

### Exercise 2

Confirm that the length of the data stored in `t_sizes` is 8. 
```{r fct_ex_2-setup}
t_sizes <- factor(c("S","S","S","M","M","M","M","L"))

```

```{r fct_ex_2, exercise = TRUE}

```

```{r fct_ex_2-solution}
length(t_sizes)

```

```{r fct_ex_2-check}
grade_code()
```

### Exercise 3

Use the `table()` function in R to output a frequency table for the data stored in the `t_sizes` variable. 

```{r fct_ex_3-setup}
t_sizes <- factor(c("S","S","S","M","M","M","M","L"))

```

```{r fct_ex_3, exercise = TRUE}

```

```{r fct_ex_3-solution}
table(t_sizes)

```

```{r fct_ex_3-check}
grade_code()
```

### Exercise 4

As we did in the introduction to R in lecture 2, create a barplot to display the data stored in the `t_sizes` variable. 
```{r fct_ex_4-setup}
t_sizes <- factor(c("S","S","S","M","M","M","M","L"))

```

```{r fct_ex_4, exercise = TRUE}

```

```{r fct_ex_4-solution}
barplot(table(t_sizes))

```

```{r fct_ex_4-check}
grade_code()
```

## Data Frames 

The exercises in this section provide some practice with the more elementary aspects of working with data frames in R. 

### Exercise 1

Consider data shown below from the Stanford University Heart Transplant Study conducted to determine whether an experimental heart transplant program increased lifespan:
```{r df_ex_1-setup}
transplant_study <- heart_transplant %>% select(-c(acceptyear, wait))
```

```{r df_ex_1, exercise = TRUE, exercise.eval = TRUE}
transplant_study
```

In this data, each of the variables shown is described as follows:

1) `id` - ID number of the patient.
2) `age` - Age of the patient at the beginning of the study.
3) `survived` - Survival status with levels alive and dead.
4) `survtime` - Number of days patients were alive after the date they were determined to be a candidate for a heart transplant until the termination date of the study
5) `prior` - Whether or not the patient had prior surgery with levels yes and no.
6) `transplant` - Transplant status with levels control (did not receive a transplant) and treatment (received a transplant).

Respond to the following quiz questions regarding the type of the variables in the `transplant_study` data. 
```{r df_variable-quiz, echo=FALSE}
quiz(
  question_checkbox("The `id` variable is best described as which type?",
    answer("Numerical Continuous"),
    answer("Numerical Discrete"),
    answer("Categorical Ordinal"),
    answer("A Unique Identifier", correct=TRUE),
    answer("Categorical Nominal"),
    answer("Categorical Binary"),
    allow_retry = TRUE
  ),
  question_checkbox("The `age` variable is best described as which type?",
    answer("Numerical Continuous"),
    answer("Numerical Discrete", correct=TRUE),
    answer("Categorical Ordinal"),
    answer("A Unique Identifier"),
    answer("Categorical Nominal"),
    answer("Categorical Binary"),
    allow_retry = TRUE
  ),question_checkbox("The `survived` variable is best described as which type?",
    answer("Numerical Continuous"),
    answer("Numerical Discrete"),
    answer("Categorical Ordinal"),
    answer("A Unique Identifier"),
    answer("Categorical Nominal"),
    answer("Categorical Binary",correct=TRUE),
    allow_retry = TRUE
  ),question_checkbox("The `survtime` variable is best described as which type?",
    answer("Numerical Continuous"),
    answer("Numerical Discrete", correct=TRUE),
    answer("Categorical Ordinal"),
    answer("A Unique Identifier"),
    answer("Categorical Nominal"),
    answer("Categorical Binary"),
    allow_retry = TRUE
  ),question_checkbox("The `prior` variable is best described as which type?",
    answer("Numerical Continuous"),
    answer("Numerical Discrete"),
    answer("Categorical Ordinal"),
    answer("A Unique Identifier"),
    answer("Categorical Nominal"),
    answer("Categorical Binary", correct=TRUE),
    allow_retry = TRUE
  )
)
```

### Exercise 2
 
Use the `$` operator to extract the `age` variable from the `transplant_study` data set as a vector. 
```{r df_ex_2-setup}
transplant_study <- heart_transplant %>% select(-c(acceptyear, wait))

```

```{r df_ex_2, exercise = TRUE}

```

```{r df_ex_2-solution}
transplant_study$age

```

```{r df_ex_2-check}
grade_code()
```

### Exercise 3

The `dim()` function returns the number of rows and columns of a data frame, for example
```{r df_ex_3a, exercise = TRUE, exercise.eval = TRUE}
dim(transplant_study)
```

The output tells us that the `transplant_study` data consists of 103 rows or observations, and  6 columns or variables. 

Use the `dim()` function to output the number of rows and columns in the `resume`` data set that records data from a study that sought to understand the influence of race and gender on job application callback rates from job postings in Boston and Chicago for several months during 2001 and 2002.
```{r df_ex_3b, exercise = TRUE}

```

```{r df_ex_3b-solution}
dim(resume)

```

```{r df_ex_3b-check}
grade_code()
```

### Exercise 4

Use the following plot to answer the quiz questions below.
```{r, echo=FALSE}
heart_transplant %>% ggplot(aes(age,survtime)) + geom_point()
```


```{r df_association-quiz, echo=FALSE}
quiz(
  question_checkbox("True or False: The plot shows a clear positive association between the `age` and `survtime` variables.",
    answer("False", correct=TRUE),
    answer("True"),
    allow_retry = TRUE
  ),
  question_checkbox("True or False: The plot shows a clear negative association between the `age` and `survtime` variables.",
    answer("False", correct=TRUE),
    answer("True"),
    allow_retry = TRUE
  )
)
```



