---
title: "Homework 2"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(learnr)
library(openintro)
library(gradethis)
tutorial_options(exercise.timelimit = 60, exercise.checker = gradethis::grade_learnr)
```


## Instructions

This homework is meant to provide practice with those aspects of R programming introduced during the second lecture. Be sure to take your time and try to understand what each of the R commands in this homework set does. 

## Using R as a calculator

The exercises in this section provide practice in using R as a simple calculator. 

### Exercise 1

Use R code to compute a value for the expression $10\left(1 - \frac{3}{2}\right)$. 


```{r calc_ex_1, exercise = TRUE}

```

```{r calc_ex_1-solution}
10*(1 - 3/2)
```

```{r calc_ex_1-check}
grade_code()
```

### Exercise 2

Use R to compute a value for the expression $2^8 - \sqrt{16}$. 

```{r calc_ex_2, exercise = TRUE}

```

```{r calc_ex_2-solution}
2^8 - sqrt(16)
```

```{r calc_ex_2-check}
grade_code()
```

### Exercise 3

Insert parentheses in the appropriate place(s) to obtain a value of 2. 

```{r calc_ex_3, exercise = TRUE, exercise.eval = TRUE}
2 * 3 +  4 * 2 - 6 / 2*3/ 2 * 5

```

```{r calc_ex_3-solution}
2 * (3 +  4 * 2 - 6 / (2*3))/ (2 * 5)

```

```{r calc_ex_3-check}
grade_code()
```


## Single-variable numerical data 

The exercises in this section provide practice with working with one-variable numerical data in R. 

### Exercise 1


### Exercise 2


### Exercise 3




## Single-variabel categorical data

The exercises in this section provide practice with working with one-variable categorical data in R. 

### Exercise 1


### Exercise 2


### Exercise 3




## Data Frames 

The exercises in this section provide some practice with the more elementary aspects of working with data frames in R. 

### Exercise 1


### Exercise 2


### Exercise 3




