---
title: "Homework 1"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(learnr)
library(openintro)
library(gradethis)
tutorial_options(exercise.timelimit = 60, exercise.checker = gradethis::grade_learnr)
```

## Instructions 

> Did you hear about the mathematician who's afraid of negative numbers? He'll stop at nothing to avoid them. 

This set of practice exercises correspond to the lecture 1 slides and Chapter 1 of the textbook [OpenIntro Statistics](https://openintro.org/book/os/). The goals for these homework exercises is for you to test your understanding of the following basic data principles and concepts:

1) Populations and samples,
2) Data organization, variables and their types, 
3) Sampling and bias, and
4) Relations between variables. 


## Exercise 1

Watch the video ["Case Study: using stents to prevent strokes"](https://www.youtube.com/watch?v=nEHFF1ADpWE) included in the lecture slides for lecture 1 and answer the following questions.  

```{r stent-visdeo-quiz, echo=FALSE}
quiz(
  question("True or False: Patients in the treatment group received medication while patients in the control group did not.",
    answer("False",correct = TRUE),
    answer("True")
  ),
  question('True or False: If you flip a coin 100 times, you should expect to land "heads" exactly 50 out of the 100 flips.',
    answer("False", correct = TRUE),
    answer("True")
  ),
  question("True or False: The observed difference between the control and treatment groups in the stent experiment may just be due to natural variation.",
    answer("False"),
    answer("True",correct = TRUE)
           )
)
```


## Exercise 2

Read Exercise 1.1 on page 11 of the textbook. Run the following R code to obtain the answer to question 1.1 (a):

```{r 1_1_a, exercise=TRUE}
(10/43)*100
```

Type in a similar R command to answer question 1.1 (b):

```{r 1_1_b, exercise=TRUE}

```


```{r 1_1_b-quiz, echo=FALSE}
quiz(
  question("What percent of patients in the acupuncture study described in Exercise 1.1 were pain free in the control group?",
    answer("about 10 percent"),
    answer("about 8 percent"),
    answer("about 4 percent", correct=TRUE),
    answer("about 2 percent")
  )
)
```

Take a minute to reflect on the answers to 1.1(a) and 1.1(b) then take the following quiz:

```{r 1_1_c-quiz, echo=FALSE}
quiz(
  question("In which group did a higher percent of patients become pain free 24 hours after receiving acupuncture?",
    answer("Control"),
    answer("Treatment", correct=TRUE)
  )
)
```

Now let's do exercise 1.1.(d):
```{r 1_1_d_quiz, echo=FALSE}
quiz(
  question("True or False: The observed difference between the control and treatment groups in the acupuncture experiment may just be due to chance.",
    answer("False"),
    answer("True",correct = TRUE)
           )
)
```


## Exercise 3

Make sure that you have read sections 1.2.1 and 1.2.2 and understand the classification of variables discussed on slide 16 of lecture 1. 

Consider the High School and Beyond dataset, stored in the openintro package. The data are stored as a data matrix or **data frame** called `hsb2`. You can read more about this dataset [here](http://openintrostat.github.io/openintro/reference/hsb2.html). Below is a preview of the dataset. You can use the arrow on the right hand side to scroll 
through the variables, and the numbers on the bottom to see different rows in 
the dataset.

```{r print-hsb2}
hsb2
```

Now, think about the variables `race`, `ses`, `schtyp`, and `prog` in the dataset. Answer the following quiz questions. 

```{r categorical-type-quiz,echo=FALSE}
quiz(
  question("The variable race is:",
    answer("categorical", correct=TRUE),
    answer("numerical")
  ),
  question("The variable ses is best decsribed as:",
    answer("categorical nominal"),
    answer("categorical binary"),
    answer("categorical ordinal", correct=TRUE)
  ),
  question("The variable schtyp is best decsribed as:",
    answer("categorical nominal"),
    answer("categorical binary", correct=TRUE),
    answer("categorical ordinal")
  ),
  question("True or False: The id column in the hsb2 data frame should not be considered as a variable.",
    answer("False"),
    answer("True", correct=TRUE)
    )
)
```


## Exercise 4

Watch the video on [Data Basics](https://www.youtube.com/watch?v=Mjif8PTgzUs) included in slide 18 of lecture 1. 

Take the following quiz:

```{r data-basics-quiz, echo=FALSE}
quiz(
  question("Which variable in the county data set discussed in the video is discrete?",
        answer("state"),
        answer("pop2010", correct=TRUE),
        answer("fed_spend"),
        answer("poverty"),
        answer("smoking_ban")
        ),
  question("True or False: The variable fed_spend is a continuous numerical variable.",
        answer("False"),
        answer("True", correct=TRUE) 
        ),
  question("True or False: If we numbered the states, the state variable would become numerical.",
        answer("False", correct=TRUE),
        answer("True")
        )
)
```


## Exercise 5

Watch the video on [Data Collection](https://www.youtube.com/watch?v=2N_bkiyTiXU) included on slide 21 of lecture 1 slides. 

```{r data-collection-quiz, echo=FALSE}
quiz(
  question("True or False: In order to avoid bias, it is essential to draw a representative sample.",
          answer("False"),
          answer("True", correct=TRUE)),
  question("True or False: When collecting data to answer a research question it is acceptable to use a convenience sample.",
           answer("False",  correct=TRUE),
          answer("True")
          )
)
```


## Exercise 6

Consider exercise 1.40 on page 37 of the textbook. Carefully examine the scatter plot shown along with the exercise in the book. Now take the following quiz:

```{r 1_40_quiz,echo=FALSE}
quiz(
  question("Which best describes the Percent with Bachelor's Degree variable?",
           answer("It is the response variable."),
           answer("It is the explanatory variable.", correct=TRUE)
           ),
  question("Which best describes the Per Capita Income variable?",
           answer("It is the response variable.", correct=TRUE),
           answer("It is the explanatory variable.")
           ),
  question("True or False: The scatter plot suggests that there is a strong linear relationship between the two variable Percent with Bachelor's Degree and Per Capita Income.",
           answer("False"),
           answer("True", correct=TRUE)
           ),
  question("True or False: We can conclude that having a bachelor's degree increases one's income.",
           answer("False", correct=TRUE),
           answer("True")
           )
)
```



## Additional Practice

For additional practice, it is recommended that you attempt the following exercises from the textbook:

1) Exercise 1.6 on page 20
2) Exercise 1.11 on page 21
3) Exercise 1.16 on page 29
4) Exercise 1.18 on page 30
5) Exercise 1.23 on page 30
6) Exercise 1.27 on page 31
7) Exercise 1.32 on page 35
8) Exercise 1.35 on page 36
9) Exercise 1.43 on page 38

