---
title: "Homework 3"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tidyverse)
library(learnr)
library(openintro)
library(gradethis)
tutorial_options(exercise.timelimit = 60, exercise.checker = gradethis::grade_learnr)
```


## Instructions 

> I ate a clock yesterday, it was very time-consuming.

The exercises in this assignment correspond to lecture 3 and section 2.1 of the textbook. 



## Scatterplots for paired numerical data

### Scatterplots with R

One way to make a scatterplot is to use the `gf_point` function from the `ggformula` package. The following code loads the `ggformula` package and makes a scatterplot of the variable `sat_m` (math SAT percentile) versus the variable `sat_v` (verbal SAT percentile) in the `satgpa` data set from the `openintro` package that complements the textbook. This data set records SAT and GPA data for 1000 students at an unnamed college.

```{r eg_scatter, message=FALSE,eval=TRUE}
library(openintro)
library(ggformula)

gf_point(sat_m~sat_v,data=satgpa)
```

The expression `sat_m~sat_v` is an example of what is called a **formula** in R. Think of the variable on the left of the formula as the $y$ variable and the variable on the right of the formula as the $x$ variable. 

### Exercise 1 a

```{r scatter_one, echo=FALSE}
quiz(
  question_checkbox("True or False: The scatter plots suggests an association between the two variables.",
    answer("False"),
    answer("True",correct = TRUE),
    allow_retry = TRUE
  )
)
```

### Exercise 1 b

Modify the following code to create a scatterplot of `fy_gpa` (first year (college) grade point average) versus `hs_gpa` (high school grade point average) from the `satgpa` data. 

```{r scatter_two, exercise = TRUE}
library(openintro)
library(ggformula)

gf_point(sat_m~sat_v,data=satgpa)
```

```{r scatter_two-solution}
library(openintro)
library(ggformula)

gf_point(fy_gpa~hs_gpa,data=satgpa)
```

```{r scatter_two-check}
grade_code()
```

### Exercise 1 c

This exercise references exercise 2.2 on page 56 of the textbook. 

```{r associations_one, echo = FALSE}
quiz(
question(
"Which statment best describes the assocaition of the variables in plot (1) of exercise 2.2?",
answer("no association"),
answer("positive association", correct = TRUE),
answer("negative association"),
allow_retry = TRUE
),
question(
"Which statment best describes the assocaition of the variables in plot (2) of exercise 2.2?",
answer("no association", correct = TRUE),
answer("positive association"),
answer("negative association"),
allow_retry = TRUE
),
question(
"Which statment best describes the assocaition of the variables in plot (3) of exercise 2.2?",
answer("no association"),
answer("positive association",correct = TRUE),
answer("negative association"),
allow_retry = TRUE
),
question(
"Which statment best describes the assocaition of the variables in plot (4) of exercise 2.2?",
answer("no association"),
answer("positive association"),
answer("negative association",correct = TRUE),
allow_retry = TRUE
)
)
```

### Exercise 1 d


```{r associations_two, echo = FALSE}
quiz(
question(
"Which statement best describes what the scatterplot suggests about the association between the two variables for first year college and high school gpa?",
answer("There is no association"),
answer("Strong positive association"),
answer("Slight positive association", correct = TRUE),
answer("Slight negative association"),
answer("Strong negative association"),
allow_retry = TRUE
)
)
```

## Dot plots and the mean

### Exercise 2 a

Using the R function `mean`, compute the mean each of the variables `sat_v`, `sat_m`, `hs_gpa`, and `fy_gpa`, in the `satgpa` data set. 

```{r mean_one-setup}
library(openintro)

```

```{r mean_one, exercise = TRUE}

```

```{r mean_one-solution}
mean(satgpa$sat_v)
mean(satgpa$sat_m)
mean(satgpa$hs_gpa)
mean(satgpa$fy_gpa)
```

```{r mean_one-check}
grade_code()
```

### Exercise 2 b

This exercise refers to problem 2.10 on page 57 of the textbook. 

## Histograms and shape




## Variance and standard deviation 




## Box plots, quartiles, and the median




## Robust statistics 




## Additional Practice

For additional practice, it is recommended that you attempt the following exercises from the textbook:

1) Exercise  on page 
2) Exercise  on page 
3) Exercise  on page 
4) Exercise  on page 
5) Exercise  on page 
6) Exercise  on page 
7) Exercise  on page 
8) Exercise  on page 
9) Exercise  on page 



